---
title: 'Exploratory Data Analysis: Bike Vendors'
author: "Katherin Jardim Rodrigues"
date: "February 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exploratory Data Analysis: Bike Vendors

##Abstract
  
Currently, we are living under an evolution from mass production to mass customization. The marketing and other operations are establishing as a goal to have one-to-one marketing. The main start point is predicting to which products a particular customer is going to be likely to respond to. Using as main source "R"" and the database "BikeVendor", we are going to build an analytic customer profile.  

##Introduction 
  
We are going to create the Analytic Customer Profile, which we can evaluate the specifics customer needs according to bike model, price and  categories. 

###Data Characteristics:


```{r libraries, error=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(httr)
library(RCurl)
```

```{r Data load, error=FALSE}
bikevendors <- read_csv("C:/Users/Katherin/Desktop/MSC ANALYTICS/ANLY506/FinalProject/Data/bikeVendors.csv")
summary(bikevendors)
rowSums(is.na(bikevendors))
colSums(is.na(bikevendors))
bikevendors[!complete.cases(bikevendors),]
```

## Including Figures


```{r figures, echo=True}
boxplot.prices <- ggplot(data = bikevendors, mapping = aes(x = category1, y = price)) +
  geom_boxplot()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
