---
title: "Code Portfolio"
author: "Katherin Jardim Rodrigues"
date: "December, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 5

Load flat files in R with the readr package: 
library(tidyverse)
read.csv() #comma delimited files
read.csv2() #reads semicolon separated files 
read_tsv() #tabs delimited files
read.delim() #reads in files with any delimiter
read_fwf() #reads fixed width files

"\n" is a convenient shortcut for adding a new line.

**What function would you use to read a file where fields were separated with "|"?**

```{r Load Data, eval = "FALSE"}
library(tidyverse)
read_delim(file, delim = "|")
```

**Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?**

-   `col_names` and `col_types`
-   `locale` determine if "." or "," is used as a decimal mark.
-   `na` and `quoted_na` missing values
-   `trim_ws` trims whitespace 
-   `n_max` rows to read
-   `guess_max` Maximum number of records to use for guessing column types
-   `progress` Display a progress bar? By default it will only display in an interactive session and not while knitting a document. The display is updated every 50,000 values and will only display if estimated reading time is 5 seconds or more. The automatic progress bar can be disabled by setting option readr.show_progress to FALSE.

Reference -> https://readr.tidyverse.org/reference/read_delim.html

**What are the most important arguments to read_fwf()?**
col_positions	
Column positions, as created by fwf_empty(), fwf_widths() or fwf_positions().

**Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you'll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame? **
```
"x,y\n1,'a,b'"
```
x <- "x,y\n1,'a,b'"
read_csv(x, quote = "'")

**Identify what is wrong with each of the following inline CSV files. What happens when you run the code?**

read_csv("a,b\n1,2,3\n4,5,6") #The first row is missing a value
read_csv("a,b,c\n1,2\n1,2,3,4") #The third column is missing a value
read_csv("a,b\n\"1") #The second column is missing a value
read_csv("a,b\n1,2\na,b") #create character table
read_csv("a;b\n1;3") #the values have semicolons instead of comma

**What are the most important arguments to locale()?**
-   date and time formats: `date_names`, `date_format`, and `time_format`
-   time zone: `tz`
-   numbers: `decimal_mark`, `grouping_mark`
-   encoding: `encoding`

**What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to ","? What happens to the default value of decimal_mark when you set the grouping_mark to "."?**
1. It's going to generate an error
2. The grouping mark will be period `"."`
3. The decimal mark will be a comma








